% !TEX root = ../report_v2.tex
\newglossaryentry{HTML}
{
    name={HTML},
    text={HTML},
    description={Hypertext Markup Language. A means of tagging text using ``markup'' to allow them to be positioned, styled and linked on web pages}
}
\newglossaryentry{JWT}
{
    name={JWT},
    text={JWT},
    description={JSON Web Tokens. A means to provide authentication over the internet using a simple string of characters}
}
\newglossaryentry{CSS}
{
    name={CSS},
    text={CSS},
    description={Cascading Style Sheet. Used for applying styles to markup text primarily displayed on web pages}
}
\newglossaryentry{VM}
{
    name={Virtual Machine},
    text={virtual machine},
    description={An abstracted virtual version of a computer. Normally runs on another host with a dedicated piece of software to manage it. Appears to the user as a real computer, however all or most components are defined by software}
}
\newglossaryentry{Bootstrap}
{
    name={Bootstrap},
    text={Bootstrap},
    description={A front end css framework designed to give developers more power with less work when creating html pages. Makes use of a standard 12-width grid system to provide an easy-to-use css styling method}
}
\newglossaryentry{API}
{
    name={API},
    text={API},
    description={Application programming interface. A set of endpoints which lead to functions and application logic. Allows developers to expose application functionality without directly exposing the code within the application}
}
\newglossaryentry{Vagrantfile}
{
    name={Vagrantfile},
    text={Vagrantfile},
    description={A template file which provides Vagrant with all the instructions required to create the desired environment. Written in the Ruby programming language}
}
\newglossaryentry{Docker container}
{
    name={Docker container},
    text={Docker container},
    description={An isolated package which bundles everything required to run an application within a container. The application can then be run within this container without regard to the underlying architecture}
}
\newglossaryentry{REST}
{
    name={REST},
    text={REST},
    description={Representational state transfer. A means of providing communication between computers across the internet. RESTful web services allow systems interact with each other using completely stateless operations}
}
\newglossaryentry{CLI}
{
    name={CLI},
    text={CLI},
    description={Command Line Interface. A means of interacting with a computer program where a user can only enter commands in the form of successive lines of text}
}
\newglossaryentry{UI}
{
    name={UI},
    text={UI},
    description={User Interface. A graphical view towards an application which exposes functionality by using buttons or other components. Typically utilised using a computer mouse}
}
\newglossaryentry{Docker}
{
    name={Docker},
    text={Docker},
    description={An application which manages containers running on a host}
}
\newglossaryentry{CRUD}
{
    name={CRUD},
    text={CRUD},
    description={Create, Read, Update, Delete. CRUD defines the four cornerstones of API functionality. An API should provide these functions to any user using the API}
}
\newglossaryentry{container}
{
    name={Container},
    text={container},
    description={An isolated piece of software bundled with everything it needs to run on the host}
}
\newglossaryentry{docker}
{
		name={Docker},
    text={Docker},
		description={A piece of software which enables orchestration and management of containers on a host}
}
\newglossaryentry{Docker host}
{
		name={Docker host},
    text={Docker host},
		description={The computer, server or virtual machine on which the Docker application is installed. One user may manage several Docker host's, depending upon how many computers they have installed it on}
}
\newglossaryentry{Docker image}
{
		name={Docker image},
		description={A template from which many containers can be started. Can be pushed an pulled to/from a remote Docker registry}
}
\newglossaryentry{Docker daemon}
{
		name={Docker daemon},
		description={The server-side component of the Docker Engine}
}
\newglossaryentry{lifecycle management}
{
		name={Lifecycle Management},
    text={lifecycle management},
		description={The management of a container over its complete lifecycle, from its beginnings as an image to starting, stopping and restarting the container and managing the interactions it has with other containers on the system}
}
\newglossaryentry{continuous integration}
{
		name={Continuos Integration},
    text={continuos integration},
		description={The act of continuously merging newly created software with the current working version, validated by automatic build and testing tools allowing for early detection of faults}
}
\newglossaryentry{continuos deployment}
{
		name={continuos deployment},
		description={The act of continuously deploying software which has passed acceptance tests to a live system}
}
\newglossaryentry{command line}
{
    name={Command Line},
    text={command line},
    description={The program through which the operating system can be interacted with. The user enters a command they wish to execute on a text line}
}
\newglossaryentry{open source}
{
    name={Open Source},
    text={open source},
    description={Software which encourages input and feedback from other developers and allows for any and all modifications to the current software package with the intent to release it under a new package}
}
\newglossaryentry{technical debt}
{
    name={Technical Debt},
    text={technical debt},
    description={The extra development work which arises as a result of implementing an easier but less robust solution}
}
\newglossaryentry{sonarqube}
{
    name={SonarQube},
    text={SonarQube},
    description={A tool to scan source code. It can inform developers of coding best-practices and highlight ``code smells'', which are essentially when best practices are not adhered to. Also highlights technical debt. Code is deemed either `passing' or `failing', meaning the code has been deemed either sufficient or insufficient in the following categories: Code Test Coverage, Bugs, Vulnerabilities and Technical Debt Ratio}
}
\newglossaryentry{Travis}
{
    name={Travis},
    text={Travis},
    description={A website which allows for automatic builds of code and feedback of results. Can be used to automatically deploy code dependent on test results also}
}
\newglossaryentry{git}
{
    name={Git},
    description={A version control system which allows source code to be tightly controlled and stored in a central repository}
}
\newglossaryentry{github}
{
    name={Github},
    text={Github},
    description={An online platform to store git repositories. Allows for multi-developer collaboration on projects}
}
\newglossaryentry{Docker Compose}
{
    name={Docker Compose},
    description={A tool developed by Docker to allow developers to easily orchestrate multi-container systems without requiring them to manually manage containers}
}
