% !TEX root = ../final_report.tex
\begin{center}
{\scshape\LARGE \textbf{Acknowledgements}\par}
\end{center}
\thispagestyle{empty}
\vspace{1cm}
I would like to sincerely thank my supervisor Dr. Brenda Mullally for her advice and support throughout this project. The guidance I received has been second to none and has made this project what it is. I also want to thank the wider computing staff - who have been instrumental in instilling a drive and hunger to learn which I did not know I had. My time at WIT will always be a fond memory due to this. 

I would also like to thank my fellow students for their help and camaraderie throughout my four years. I have made some great friendships in my time at WIT which I know will last beyond my time here.

To Leigh Griffin, David Martin and indeed Red Hat Mobile in general I want to express my deepest gratitude. You have equipped me with tools seldom found in the lecture hall. To say I am a better developer as a result of your input and guidance is a gross understatement.

To my sister Emily, thank you for your support and encouragement over the last four years. To my parents John and Sylvia, thank you for everything. Your unwavering belief in me has been a deep source of motivation.

Finally, to Denise, you have been my source of inspiration over these past four years. I could not have asked for a better person to read all the boring papers I wrote and to listen intently to me drone on for hours at a time. For that I am eternally grateful. We can finally have our weekends back now, I promise.

\clearpage
